\section{Introduction}
\label{sec:intro}
%
Operating Systems (OS) is a piece of software that manages and virtualizes hardware for applications.
%
As OS abstracts away the complexity of orchestrating various hardware components such as CPUs, Memory, and I/O as well as different applications, it has been instrumental in reducing the burden of the programmers.
%
Virtualization refers to adding another level of indirection to run OSes on an abstraction of hardware such as CPUs, GPUs, and FPGAs.
%
However, the virtualization can not only be categorized by the target platform it virtualizes but also at which level it virtualizes the system.
%
For example, the 1st Generation Virtual Machine (VM) is abstraction between OS and hardware, and OS were installed on these virtual hardware.
%
2nd Generations Container is an abstraction between the servers and the OS, and it allows the OS to run multiple isolated user-space applications on the host OS.
%
As VM runs a complete OS on emulated hardware, it is too heavy to scale.
%
On the other hand, the Containers does not provide as strong security boundaries as VMs.
%
Between the spectrum of these two major types is the Light VM, which strikes balance between security and performance.
%

The aim of the work is to provide a variety of performance measurements to analyze the performance of different types of virtualization: VM, Light VM, and Containers.
%
We first selected gVisor as a benchmark to analyze the different parts of the systems such as CPU and memory performance.
%
We also evaluated the three different virtualization using achine learning workload on TensorFlow and ffmpeg.
%

INSIGHT INSIGHT

%
To this end, this report makes the following contributions:

\begin{enumerate}

\item We compare the performance of different virtualization schemes on the gVisor benchmark and analyze them to better understand the overheads
\item We also measure real life applications on different virtualization schemes on the spectrum to understand their implication in real applications

\end{enumerate}

All the experiment scripts, experimental results, and in-depth analysis are available in \url{https://github.com/jkim796/vm-measurements}.
